Interval Probability for Fuzzy Quantum Theories

### 2016-05-15 prob.tex
prob.tex \section{Quantum Probability Spaces} updates...

\begin{definition}[Projection Operators; Orthogonality~\cite{10.2307/2308516,Redhead1987-REDINA,peres1995quantum,Swart2013}]
\label{def:Projection} Given a Hilbert space $\Hilb$, an event\footnote{An event
is formally called an experimental proposition~\cite{BirkhoffVonNeumann1936}, a question~\cite{10.2307/2308516,DBLP:journals/corr/abs-0910-2393}, or an
elementary quantum test~\cite{peres1995quantum}} mathematically is represented as a projection operator $P:\Hilb\rightarrow\Hilb$ onto a linear subspace~$S$ of $\Hilb$. The set of all
events can be defined recursively as follow:
\footnote {``Projection'' is sometimes called
``orthogonal projection" or ``self-adjoint projection" to
emphasize $P^{\dagger} = P$~\cite{Maassen2010}.}
\begin{itemize}
\item $\mathbb{0}$ and $\mathbb{1}$ are a projection. 
\item For any pure state~$\ket{\psi}$, $\proj{\psi}$ is a projection
operator. 
\item Projection operators $P_1$ and $P_2$ are orthogonal if $P_1P_2 =
  P_2P_1 = \mathbb{0}$. The sum of two orthogonal projections~$P_{1}\tensor*[_{\mathscr{O}}]{+}{}P_{2}$
is also a projection, where the preposing subscript $\mathscr{O}$
means $\tensor*[_{\mathscr{O}}]{+}{}$ is an operation between operators,
and may be dropped when summands are clearly operators. 
\item For any pure state~$\ket{\psi}$, $\proj{\psi}$ is a projection
operator. Conversely, every projection~$P$ can be expressed as $\sum_{j}\proj{\psi_{j}}$,
where $P$ actually projects onto the linear subspace~$S$ which
has an orthonormal basis~$\{\ket{\psi_{j}}\}$. 
\end{itemize}
\end{definition}

@@

\begin{definition}[Quantum Probability Space~\cite{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010}]
  Given a Hilbert space $\Hilb$, a \emph{quantum probability space}
  consists of a set of events $\events$ and a probability measure
  $\mu : \events \rightarrow [0,1]$ such that:\footnote {It is
    possible to define a more general space of events consisting of
    all operators~$\mathcal{A}$ on $\Hilb$ and consider
    $\mu:\mathcal{A}\rightarrow\C$~\cite{Maassen2010,Swart2013}.  When
    an operator $A\in\mathcal{A}$ is Hermitian, $\mu\left(A\right)$ is
    the expectation value of $A$. We does not take this approach
    because we want to focus only on probability. }
\begin{itemize}
\item The set of events consists of all projections as in
  definition~\ref{def:Projection};
\item $\mu(\mathbb{1})=1$, and 
\item for mutually orthogonal projections $E_{i}$, we have $\mu\left(\tensor*[_{O}]{\sum}{_{i}}E_{i}\right)=\tensor*[_{\mathbb{R}}]{\sum}{_{i}}\mu\left(E_{i}\right)$,
where $\tensor*[_{O}]{\sum}{_{i}}$ specifies that we add operators,
and the preposing $O$ may be dropped when summands are clearly operators.
\end{itemize}
\qed\end{definition}

Comparing to the classical probability space, the empty set~$\emptyset$
corresponds to the empty projection~$\mathbb{0}$ and the event of
whole sample space~$\Omega$ corresponds to the identity projection~$\mathbb{1}$.
In contrast, the union~$\cup$ of any two events always gives an
event classically, the operator addition~$\tensor*[_{\mathscr{O}}]{+}{}$
of two projections may not be a projection. As the result, the equation
$\pmeas(E_{1}\cup E_{2})=\pmeas(E_{1})\tensor*[_{\mathbb{R}}]{+}{}\pmeas(E_{2})$
is always defined, and it is true when $E_{1}$ and $E_{2}$ are disjoint;
however, $\mu\left(E_{1}\tensor*[_{\mathscr{O}}]{+}{}E_{2}\right)=\mu(E_{1})\tensor*[_{\mathbb{R}}]{+}{}\mu(E_{2})$
is always true whenever the left-handed side is defined. Whether equation
is defined also effects the further properties of quantum probability
space.

\begin{definition}{[}Orthogonal Complement; Commutativity~\cite{peres1995quantum}{]} 
\begin{itemize}
\item If $P$ is a projection operator, then $\mathbb{1}\tensor*[_{O}]{-}{}P$
is also a projection operator.
\end{itemize}
Projection operators $P_1$ and $P_2$ commute if $P_1P_2 =
  P_2P_1$;
If the projections $P_1$ and $P_2$ commute then $P_1P_2$ is also
  a projection. Moreover, if $P_1$ and $P_2$ project onto
  subspaces $S_1$ and $S_2$ respectively, then $P_1P_2$ will project onto the
  intersection of $S_1$ and $S_2$, i.e., $S_1 \cap S_2$.
\end{definition}

>>>>

\begin{definition}[Projection Operators; Orthogonality~\cite{10.2307/2308516,Redhead1987-REDINA,peres1995quantum,Swart2013}]
\label{def:Projection} Given a Hilbert space $\Hilb$, an event\footnote{An event
is formally called an experimental proposition~\cite{BirkhoffVonNeumann1936}, a question~\cite{10.2307/2308516,DBLP:journals/corr/abs-0910-2393}, or an
elementary quantum test~\cite{peres1995quantum}} mathematically is represented as a projection operator $P:\Hilb\rightarrow\Hilb$ onto a linear subspace~$S$ of $\Hilb$. The set of all
events can be defined recursively as follow:
\footnote {``Projection'' is sometimes called
``orthogonal projection" or ``self-adjoint projection" to
emphasize $P^{\dagger} = P$~\cite{Maassen2010}.}
\begin{itemize}
\item $\mathbb{0}$ is a projection. 
\item For any pure state~$\ket{\psi}$, $\proj{\psi}$ is a projection
operator. 
\item Projection operators $P_1$ and $P_2$ are orthogonal if $P_1P_2 =
  P_2P_1 = \mathbb{0}$. The sum of two orthogonal projections~$P_{1}\tensor*[_{\mathscr{O}}]{+}{}P_{2}$
is also a projection, where the preposing subscript $\mathscr{O}$
means $\tensor*[_{\mathscr{O}}]{+}{}$ is an operation between operators,
and may be dropped when summands are clearly operators. 
\item Conversely, every projection~$P$ can be expressed as
$\tensor*[_{\mathscr{O}}]{\sum}{_j}\proj{\psi_{j}}$,
where $P$ actually projects onto the linear subspace~$S$ which
has an orthonormal basis~$\{\ket{\psi_{j}}\}$. 
\end{itemize}
\qed\end{definition}

@@

\begin{definition}[Quantum Probability Space~\cite{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010}]
  Given a Hilbert space $\Hilb$, a \emph{quantum probability space}
  consists of a set of events $\events$ and a probability measure
  $\mu : \events \rightarrow [0,1]$ such that:\footnote {It is
    possible to define a more general space of events consisting of
    all operators~$\mathcal{A}$ on $\Hilb$ and consider
    $\mu:\mathcal{A}\rightarrow\C$~\cite{Maassen2010,Swart2013}.  When
    an operator $A\in\mathcal{A}$ is Hermitian, $\mu\left(A\right)$ is
    the expectation value of $A$. We does not take this approach
    because we want to focus only on probability. }
\begin{itemize}
\item $\mu(\mathbb{1})=1$, and 
\item for mutually orthogonal projections $E_{i}$, we have 
$\mu\left(\tensor*[_{\mathscr{O}}]{\sum}{_{i}}E_{i}\right)=\tensor*[_{\mathbb{R}}]{\sum}{_{i}}\mu\left(E_{i}\right)$.
\end{itemize}
\qed\end{definition}

Comparing to the classical probability space, the empty set~$\emptyset$
corresponds to the empty projection~$\mathbb{0}$ and the event of
whole sample space~$\Omega$ corresponds to the identity projection~$\mathbb{1}$.
In contrast, the union~$\cup$ of any two events always gives an
event classically, but the operator addition~$\tensor*[_{\mathscr{O}}]{+}{}$
of two projections may not be a projection. As the result, the classical
condition~$\pmeas(E_{1}\cup E_{2})=\pmeas(E_{1})\tensor*[_{\mathbb{R}}]{+}{}\pmeas(E_{2})$
is always defined, and it is true when $E_{1}$ and $E_{2}$ are disjoint;
however, $\mu\left(E_{1}\tensor*[_{\mathscr{O}}]{+}{}E_{2}\right)=\mu(E_{1})\tensor*[_{\mathbb{R}}]{+}{}\mu(E_{2})$
is always true whenever the left-handed side is defined. Whether equation
is defined also effects the further properties of quantum probability
space.

\begin{definition}{[}Orthogonal Complement; Commutativity~\cite{peres1995quantum}{]} 
\begin{itemize}
\item If $P$ is a projection operator, then $\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}P$
is also a projection operator. It is orthogonal to $P$, $\mu\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}P\right)=1\tensor*[_{\mathbb{R}}]{-}{}\mu\left(P\right)$,
and it corresponds to the complement event~$\Omega\backslash E$
in classical probability.
\end{itemize}
Projection operators $P_1$ and $P_2$ commute if $P_1P_2 =
  P_2P_1$;
If the projections $P_1$ and $P_2$ commute then $P_1P_2$ is also
  a projection. Moreover, if $P_1$ and $P_2$ project onto
  subspaces $S_1$ and $S_2$ respectively, then $P_1P_2$ will project onto the
  intersection of $S_1$ and $S_2$, i.e., $S_1 \cap S_2$.
\qed\end{definition}
